---
title: "factor_1"
author: "Erica"
date: "12/30/2020"
output: html_document
---

## Scrape [companies with CMMI](https://cmmiinstitute.com/pars/?StateId=c2c50afd-1884-4a85-9665-57d0a50a0e1c&PageNumber=1&Handler=ApplyFilters) and clean to select only CMMI ML3, ML4, and ML5

### Load packages
```{r cmmi}

library(rvest)
library(pander)
library(xml2)
library(tidyverse)

```

### Web scraping and data cleaning
```{r }

# Scrape whole item-card data from all pages; separate into 500 pages at the time so code runs faster
itemcard_1_500 <- lapply(paste0('https://cmmiinstitute.com/pars/?StateId=33296d0d-c5c5-4d47-b36b-c692d73a5ab7&PageNumber=', 1:500),
                function(url){
                  url %>% read_html() %>% 
                    html_nodes("div.item-card") %>% 
                    html_text()
                })

itemcard_501_1000 <- lapply(paste0('https://cmmiinstitute.com/pars/?StateId=33296d0d-c5c5-4d47-b36b-c692d73a5ab7&PageNumber=', 501:1000),
                function(url){
                  url %>% read_html() %>% 
                    html_nodes("div.item-card") %>% 
                    html_text()
                })

itemcard_1001_1500 <- lapply(paste0('https://cmmiinstitute.com/pars/?StateId=33296d0d-c5c5-4d47-b36b-c692d73a5ab7&PageNumber=', 1001:1500),
                function(url){
                  url %>% read_html() %>% 
                    html_nodes("div.item-card") %>% 
                    html_text()
                })

itemcard_1500_1913 <- lapply(paste0('https://cmmiinstitute.com/pars/?StateId=33296d0d-c5c5-4d47-b36b-c692d73a5ab7&PageNumber=', 1501:1913),
                function(url){
                  url %>% read_html() %>% 
                    html_nodes("div.item-card") %>% 
                    html_text()
                })

# turn lists into dfs
df_1_500 <- as.data.frame(do.call(rbind, lapply(itemcard_1_500, as.data.frame)))
df_501_1000 <- as.data.frame(do.call(rbind, lapply(itemcard_501_1000, as.data.frame)))
df_1001_1500 <- as.data.frame(do.call(rbind, lapply(itemcard_1001_1500, as.data.frame)))
df_1501_1913 <- as.data.frame(do.call(rbind, lapply(itemcard_1500_1913, as.data.frame)))

# bind dfs consecutively
df_1_1000 <- rbind(df_1_500, df_501_1000)
df_1_1500 <- rbind(df_1_1000, df_1001_1500)
df_1_1913 <- rbind(df_1_1500, df_1501_1913)

# remove unnecesary dfs after done
rm(df_1_500)
rm(df_501_1000)
rm(df_1001_1500)
rm(df_1501_1913)
rm(df_1_1000)
rm(df_1_1500)

# work with df_1_1913

df <- df_1_1913

# remove repeating "[\r\n]" character
orgs1 <- trimws(gsub("[\r\n]", "", df$`X[[i]]`))
df$`X[[i]]` <- orgs1
colnames(df) <- "x"

# separate organization/company name from the rest of the text per row entry
df1 <- df %>% separate(
  col = x,
  into = c("org", "id_level"),
  sep = ":",
  remove = TRUE,
  convert = FALSE,
  extra = "warn",
  fill = "warn"
)

```


### Assign SAM status, CMMI level, and other data cleaning. Search for "with SAM" or "without SAM" from the company entry and create a new column that designates the "SAM status" of the company. Repeat for ML2-5 to designate "CMMI level"
```{r}

# separate out SAM, levels, etc.
df1$sam_status <- ifelse(grepl("with SAM",df1$id_level),'with SAM',
                         ifelse(grepl("without SAM", df1$id_level), 'without SAM', 'something_else'))

df1$level_status <- ifelse(grepl("ML3",df1$id_level),'ML3',
                           ifelse(grepl("ML2",df1$id_level),'ML2',
                                  ifelse(grepl("ML5",df1$id_level),'ML5',
                                         ifelse(grepl("ML4",df1$id_level),'ML4', 'something_else'))))

# remove out "ID" from org name
df2 <- df1 %>% separate(
  col = org,
  into = c("org", "null"),
  sep = "ID",
  remove = TRUE,
  convert = FALSE,
  extra = "warn",
  fill = "warn"
)

df2$null <- NULL

# add CMMI-SVC or -DEV; may not be needed
df2$cmmi_type <- ifelse(grepl("CMMI-SVC",df2$id_level),'CMMI-SVC',
                         ifelse(grepl("CMMI-DEV", df2$id_level), 'CMMI-DEV', 'something_else'))

df2 <- df2[-1369,] # weird company, no relevant data

# fix ids to add; not necessary right now
df2$id <- trimws(df2$id)
id_extracted <- str_extract_all(df2$id, "0.|1.|2.|3.|4.|5.|6.|7.|8.|9.")
id_str <- trimws(id$id)
df2$id_ex <- id_ex
id_ex_v2 <- trimws(gsub("#first term ends in space, . , or - ", "", df2$id_ex))


# create a new df with company name, sam status, cmmi level, and cmmi type
cmmi <- df2 %>% select(org, sam_status, level_status, cmmi_type)

```


### Select  companies with >= ML3 and with SAM
```{r}

# select SAM with >= ML3
cmmi_sam_ml3 <- cmmi %>% filter(grepl("with SAM", cmmi$sam_status), grepl(c("ML3"), cmmi$level_status))
cmmi_sam_ml4 <- cmmi %>% filter(grepl("with SAM", cmmi$sam_status), grepl(c("ML4"), cmmi$level_status))
cmmi_sam_ml5 <- cmmi %>% filter(grepl("with SAM", cmmi$sam_status), grepl(c("ML5"), cmmi$level_status))

cmmi_final <- rbind(cmmi_sam_ml3, cmmi_sam_ml4, cmmi_sam_ml5)

# export to Excel
library(writexl)
write_xlsx(cmmi_final, "cmmi_2021_sam_ML3_ML4_ML5_world.xlsx")


```


